Sperm should evolve to make female meiosis fair.

### 2014-05-17 writeup_and_notes/male_dependent_drive.tex
yb read text through the end of the discussion

Why is it that an allele that biases female meiosis in its favor can generate a genetic conflict, but an allele in sperm that assists this female driver cannot? 
So long as the transmission advantage of female meiotic drive outweigh the organismal fitness cost to heterozygotes the female driver can spread when rare, and it increases in 		
	frequency until the fitness cost experienced when homozygous balances the transmission advantage.
By contrast a sperm promotor of female drive is only effective when matched with a heterozygote female -- meaning that when rare this allele rarely enhances female drive. 
Even worse, when it does so it will preferentially find itself in a low fitness drive homozygote. 
Not only are drive-promoting sperm alleles unable to create a sustained genetic conflict, 
	but alleles in sperm with the opposite effect - that is those that prevent their own drive through female meiosis do maintain a polymorphisms and 
	provide evolution  with time and opportunity to further minimize drive.
This is because such drive suppressing alleles reduced their chances
of forming low fitness homozygotes. 
In fact, an allele in sperm which causes the alternate allele to drive can be favored, a counterintuitive result 
	consistent with the tenuous evidence that the non-driving
        $ln^-$ allele is over transmitted through female meiosis in $ln^-/ln^+$ heterozygote when fertilized by $ln^+$
        sperm \cite{agulnick, Pomiankowski1993}.   
More generally, alleles that act through sperm to
 reduce the opportunity of female meiotic drive regardless of linkage or phase.

>>>>

Why is it that an allele that biases female meiosis in its favor can generate a genetic conflict, but an allele in sperm that assists this female driver cannot? 
So long as the transmission advantage of female meiotic drive outweigh the organismal fitness cost to heterozygotes the female driver can spread when rare, and it increases in 		
	frequency until the fitness cost experienced when homozygous balances the transmission advantage.
By contrast a sperm promotor of female drive is only effective when matched with a heterozygote female -- meaning that when rare this allele rarely enhances female drive. 
Even worse, when it does so it will preferentially find itself in a low fitness drive homozygote. 
Not only are drive-promoting sperm alleles unable to create a sustained genetic conflict, 
	but alleles in sperm with the opposite effect - that is those that prevent their own drive through female meiosis do maintain a polymorphisms and 
	provide evolution  with time and opportunity to further minimize drive.
This is because such drive suppressing alleles reduced their chances
of forming low fitness homozygotes. 
%In fact, an allele in sperm which causes the alternate allele to drive can be favored, a counterintuitive result 
%	consistent with the tenuous evidence that the non-driving
%        $ln^-$ allele is over transmitted through female meiosis in $ln^-/ln^+$ heterozygote when fertilized by $ln^+$
%        sperm \cite{agulnick, Pomiankowski1993}.   
% YB - WE DID NOT TALK ABOUT THIS IN THE RESULTS [ALTHOUGH IT'S TRUE... PERHAPS TOO DISTRACTING]
More generally, alleles that act through sperm to
 reduce the opportunity of female meiotic drive regardless of linkage or phase.
